Results Coding

### 2023-12-11 analysis/practiceCoding_AW.Rmd
Code cleaning
removed redundant and irrelevant code chunks and reorganised into more logical sequence

@@

# Journal Policy Overview
```{r}

d_journals_anyPPC <- d_journals %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == "TRUE")

@@

``` {r}

d_journalsEmp <- d_journals %>%
  filter(is_empirical == "TRUE") %>%
  filter(ppc_type == "A")

table(d_journalsEmp$field, d_journalsEmp$sample_id)

@@

# Create tibbles for prominent and random journal samples
```{r}
dj_prom <- d_journalsEmp %>%
  mutate(sample_id = case_when(
    sample_id == "both" ~ "prominent",
    TRUE ~ sample_id
  )) %>%
  filter(sample_id == "prominent")

dj_random <- d_journalsEmp %>%
  mutate(sample_id = case_when(
    sample_id == "both" ~ "random",
    TRUE ~ sample_id
  )) %>%
  filter(sample_id == "random")
```

# Descriptives for each journal sample 
```{r}
table(dj_prom$field, dj_prom$has_ppc)
table(dj_random$field, dj_random$has_ppc)

table(dj_prom$field, dj_prom$cope)
table(dj_random$field, dj_random$cope)
```

# Plot sample id by field
```{r}

d_journals %>%
  ggplot() +
  geom_bar(
    mapping = aes(x = field, fill = sample_id),
    stat = "count",
    position = "stack",
    colour = "black",
    just = 0.5,
    width = 0.7,
    na.rm = FALSE,
    orientation = NA,
    show.legend = TRUE,
    inherit.aes = TRUE
  ) +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(title = "Sample ID by Field", x = "Field", y = "Count")

@@

# CHAT GPT TEST
```{r}
library(dplyr)
library(ggplot2)

d_journals %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
  )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc %in% c("YES", "NO")) %>%
  filter(sample_id == 'both' | sample_id == 'random') %>%
  group_by(field, has_ppc) %>%  # Group by field and has_ppc
  summarise(count = n()) %>%   # Calculate counts for each combination
  group_by(field) %>%           # Group by field only
  mutate(percentage = round(count / sum(count) * 100)) %>%  # Calculate percentages within each field and round
  ggplot() +
  geom_bar(
    mapping = aes(x = field, y = count, fill = has_ppc),
    stat = "identity",  # Use "identity" for y values
    position = "stack",
    colour = "black",
    width = 0.7,
    na.rm = FALSE,
    orientation = NA,
    show.legend = TRUE,
    inherit.aes = TRUE
  ) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Random Journal PPC Acceptance by Field", x = "Field", y = "Count")

# Create bar plot of PPC policy by Field
```{r}

# Creates bar graph for Prominent journals

d_journals %>%  
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  filter(sample_id == 'both' | sample_id == 'prominent') %>%
  ggplot() +
geom_bar(
  mapping = aes(x=field, fill = has_ppc),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Prominent Journal PPC Acceptance by Field", x = "Field", y = "Count")
```

# Creates bar graph for Random journals
``` {r}
d_journals %>%  
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'YES',
    has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
    )) %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES" | has_ppc == "NO") %>%
  filter(sample_id == 'both' | sample_id == 'random') %>%
  ggplot() +
geom_bar(
  mapping = aes(x=field, fill = has_ppc),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(title = "Random Journal PPC Acceptance by Field", x = "Field", y = "Count")
```

# Plot PPC length limits by Field and COPE
```{r}
d_length <- d_journals %>%
  select(has_ppc, journal_name, jif, cope, ppc_length, ppc_time, ppc_ref, field) %>%
  filter(has_ppc=="YES") %>%
  filter(ppc_length !="NOT STATED") %>%
  filter(ppc_length !="Qualitative limit")

d_length$ppc_length <- as.numeric(d_length$ppc_length)

d_length %>%
ggplot() +
  geom_point(aes(x = ppc_length, 
                               y = jif,
                              shape = cope, 
                              colour = field,
                              size=1, 
                              alpha = 0.7, 
                              show.legend = FALSE,
                              inherit.aes = FALSE)) +
  theme_grey() +
  labs(title = "Word Limits by JIF where PPC Accepted", x = "Word Limits", y = "Journal Impact Factor") +
  scale_fill_brewer(palette="Accent") 
```

# Calculate CIs for YES 
Not sure if this makes sense to do for Prominent and Total, as these are not random samples
```{r}
library(binom)

@@

# Calculate CIs for NO 
```{r}
library(binom)

@@

table(d_journals$ppc_name)  #PPCnames
table(d_journals$sample_id, d_journals$ppc_name) #lists journals with PPC types

@@

# Look at PPC length limitations
```{r}

# Removes journals that do not offer any PPC 
 d_PPConly <- d_journals %>%
   filter(has_ppc == "YES")

#Look at stated length limits
PPC_length <- d_PPConly %>%
  filter(!is.na(ppc_length)) %>%
  filter(ppc_length != "NO") %>%
  filter(ppc_length != "NOT STATED")

dj_prominent <- d_journals %>%
  filter(sample_id != "random")

dj_random <- d_journals %>%
  filter(sample_id != "prominent")

#table_length <- table(PPC_length$ppc_length, PPC_length$ppc_name)
table(dj_prominent$ppc_length, dj_prominent$ppc_name)
table(dj_random$ppc_length, dj_random$ppc_name)
```

# Mean JIF by field and sample
```{r}

dj_prom %>%
  filter(ppc_type == "A") %>%
  group_by(field) %>%
  summarise(mnJIF = mean(jif)) %>%
  ungroup()

dj_prom %>%
  filter(ppc_type == "A") %>%
  mutate(jif = round(jif, 2)) %>%
  summarise(mean(jif), median(jif))

@@

```{r}
dj_random %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  group_by(field) %>%
  summarise(mnJIF = mean(jif)) %>%
  ungroup()

dj_random %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  mutate(jif = round(jif, 2)) %>%
  summarise(mean(jif), median(jif))
```
# PPC and COPE
```{r}

table(dj_prom$has_ppc, dj_prom$cope)

dj_rand <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == TRUE)

table(dj_rand$has_ppc, dj_rand$cope)

@@

# Look at PPC time limitations
``` {r}

table(dj_prominent$ppc_time, dj_prominent$ppc_name)
table(dj_random$ppc_time, dj_random$ppc_name)

```
CREATE FIGURES FOR TYPES OF RESTRICTION STATEMENTS

# FIGURE of PROMINENT length limits
```{r}

dj_prominent %>%
  filter(!is.na(ppc_length)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ "Quantitative",
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_length)
  )) %>%
  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Prominent_length.png", plot = last_plot(), device = "png")
```
# FIGURE of PROMINENT time limits
```{r}

dj_prominent %>%
  filter(!is.na(ppc_time)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ "Quantitative",
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_time)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_time, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "Time-to-Submit Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Prominent_time.png", plot = last_plot(), device = "png")
```
# FIGURE of PROMINENT reference limits
```{r}

dj_prominent %>%
  filter(!is.na(ppc_ref)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_ref = case_when(
    ppc_ref %in% c(10, 15, 20, 5, "max 20") ~ "Quantitative",
    ppc_ref == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_ref)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_ref, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "Reference Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Prominent_ref.png", plot = last_plot(), device = "png")
```
# FIGURE of PROMINENT Peer-Review 
```{r}

dj_prominent %>%
  filter(!is.na(ppc_review)) %>%
  filter(has_ppc != "ARCHIVE") %>%
 mutate(ppc_review = fct_relevel(
    case_when(
      ppc_review == "YES" ~ "Yes",
      ppc_review == "NO" ~ "No",
      ppc_review == "NOT STATED" ~ "Not Stated",
      TRUE ~ as.character(ppc_review)  # Keep other values as they are
    ),
    c("Not Stated", "No", "Yes")  # Specify the desired order
  )) %>%
  ggplot(mapping = aes(x = ppc_review, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "PPC Sent for Peer-review", y = "Count", fill = "PPC Type")

ggsave(filename = "Prominent_review.png", plot = last_plot(), device = "png")
```

# FIGURE of RANDOM Length Limits
```{r}

dj_random %>%
  filter(!is.na(ppc_length)) %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 2000, 2500, 2650, 500) ~ "Quantitative",
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_length)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 25)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.7)) +
  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Random_length.png", plot = last_plot(), device = "png")
```

# FIGURE of RANDOM time limits
```{r}

dj_random %>%
  filter(!is.na(ppc_time)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% 39.15 ~ "Quantitative",
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_time)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_time, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 25)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.7)) +
  labs(x = "Time-to-Submit Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Random_time.png", plot = last_plot(), device = "png")
```
# FIGURE of PROMINENT reference limits
```{r}

dj_random %>%
  filter(!is.na(ppc_ref)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_ref = case_when(
    ppc_ref %in% c(10, 15, 5) ~ "Quantitative",
    ppc_ref == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_ref)  # Keep other values as they are
  )) %>%
  ggplot(mapping = aes(x = ppc_ref, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 25)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.7)) +
  labs(x = "Reference Limit Statement", y = "Count", fill = "PPC Type")

ggsave(filename = "Random_ref.png", plot = last_plot(), device = "png")
```
# FIGURE of RANDOM Peer-Review 
```{r}

dj_random %>%
  filter(!is.na(ppc_review)) %>%
  filter(has_ppc != "ARCHIVE") %>%
 mutate(ppc_review = fct_relevel(
    case_when(
      ppc_review == "YES" ~ "Yes",
      ppc_review == "NO" ~ "No",
      ppc_review == "NOT STATED" ~ "Not Stated",
      TRUE ~ as.character(ppc_review)  # Keep other values as they are
    ),
    c("Not Stated", "No", "Yes")  # Specify the desired order
  )) %>%
  ggplot(mapping = aes(x = ppc_review, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5,
           ) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 25)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.7)) +
  labs(x = "PPC Sent for Peer-review", y = "Count", fill = "PPC Type")

ggsave(filename = "Random_review.png", plot = last_plot(), device = "png")
```

@@

# Presentation Graph of PPC by Sample

# Articles and Prevalence

# Calculate CIs for NO 
```{r}
library(binom)

# Prominent Sample data for linked
plPPCsuccess <- 1
rlPPCsuccess <- 0
linkedSample <- 101

```
```{r}
library(dplyr)
library(ggplot2)
library(forcats)

# Modify the dataset to ensure "both" values are included in both "Prominent" and "Random"
d_journals_processed <- d_journals %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
  )) %>%
  filter(ppc_type == "A") %>%
  filter(is_empirical == TRUE) %>%
  mutate(sample_id = fct_recode(sample_id, 
                                "Prominent" = "prominent", 
                                "Random" = "random",
                                "Both" = "both"))

# Create a summary dataset to count "both" values in both "Prominent" and "Random"
summary_data <- d_journals_processed %>%
  filter(sample_id %in% c("Prominent", "Random")) %>%
  group_by(has_ppc, sample_id) %>%
  summarise(count = sum(count)) %>%
  ungroup()

# Create the ggplot with count labels
ggplot(data = summary_data) +
  geom_bar(
    mapping = aes(x = has_ppc, y = count, fill = sample_id),
    stat = "identity",  # Use stat = "identity" to specify y as the count values
    position = position_dodge(width = 0.8),
    colour = "black",
    alpha = 0.7,
    width = 0.7,
    na.rm = FALSE,
    orientation = "vertical",
    show.legend = TRUE,
    inherit.aes = TRUE
  ) +
  geom_text(
    aes(x = has_ppc, y = count, label = count, group = sample_id),
    position = position_dodge(width = 0.8),
    vjust = -0.5,
    size = 4
  ) +
  theme_bw() +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Journal PPC Acceptance by Sample",
       x = "Accepts PPC",
       y = "Count",
       fill = "Sample Type"
  ) + 
  theme(
    text = element_text(size = 18)
  )

# Save the plot
ggsave(filename = "PPCbySample.png", plot = last_plot(), device = "png")

```
# Restriction Statements Graph
```{r}

@@

# Check median and IQR for each field
```{r}

# Group the tibble by the 'field' column
prom_grouped <- dj_prom %>% group_by(field)

#For randomly sampled journals 
``` {r}
# Group the tibble by the 'field' column
rand_grouped <- dj_rand %>% filter(!is.na(jif)) %>% group_by(field)

dj_rand %>%
   filter(!is.na(jif)) %>%
  mutate(jif = round(jif, 2)) %>%
  summarize(
    mean_jif = mean(jif),
    median_jif = median(jif),
    q1_jif = quantile(jif, 0.25),
    q3_jif = quantile(jif, 0.75),
    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
    count = n()
  )

```
```{r}
count_non_missing <- sum(!is.na(dj_prominent$ppc_length))
cat("Count of non-missing values in ppc_length:", count_non_missing, "\n")
```

@@

COMPARING SAMPLES TO EACH OTHER ON PPC ACCEPTANCE
```{r}

dj_prom %>%
mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
  ))

dj_rand %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' | has_ppc == 'NO EXPLICIT' | has_ppc == 'NO IMPLICIT' ~ 'NO',
    TRUE ~ has_ppc
  ))

chisq.test(x=dj_prom$has_ppc, y=dj_rand$has_ppc)

prop.test()

```
```{r}
# Sample data
yes_prom <- 38  # Number of "yes" responses in Sample 1 (dj_prom)
yes_rand <- 23  # Number of "yes" responses in Sample 2 (dj_rand)

# Total number of observations in each sample (assuming 100)
n_prom <- 100
n_rand <- 100

# Perform the proportion test
test_result <- prop.test(x = c(yes_prom, yes_rand), n = c(n_prom, n_rand), alternative = "two.sided")

# Print the test result
print(test_result)

@@

>>>>

```
# Create separate tibbles for Prominent and Randomly-selected journal samples
```{r}
dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```
# DESCRIPTIVE STATISTICS

# JIF median and IQR (prominent sample)
```{r}

# Calculate mean and median JIF for entire prominent sample
dj_prominent %>%
  filter(ppc_type == "A") %>%
  mutate(jif = round(jif, 2)) %>%
  summarise(mean(jif), median(jif))
```

# JIF median and IQR by subfield (prominent sample)
```{r}
# Group the tibble by the 'field' column
prom_grouped <- dj_prominent %>% 
  filter(ppc_type == "A") %>%
  group_by(field)

# JIF median and IQR (random sample)
``` {r}
# Calculate mean and median JIF for entire random sample
dj_random %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>%
  mutate(jif = round(jif, 2)) %>%
  summarise(mean(jif), median(jif))
```

# JIF median and IQR by subfield (random sample)
```{r}
# Group the tibble by the 'field' column
rand_grouped <- dj_random %>% 
  filter(ppc_type == "A") %>%
  filter(!is.na(jif)) %>% 
  group_by(field)

dj_random %>%
   filter(!is.na(jif)) %>%
  mutate(jif = round(jif, 2)) %>%
  summarize(
    mean_jif = mean(jif),
    median_jif = median(jif),
    q1_jif = quantile(jif, 0.25),
    q3_jif = quantile(jif, 0.75),
    iqr_jif = quantile(jif, 0.75) - quantile(jif, 0.25),
    count = n()
  )

@@

# Journal PPC Policy Overview
```{r}

d_journals_anyPPC <- d_journals %>%
  filter(ppc_type == "A") %>% # Filters to a single row for each journal
  filter(is_empirical == "TRUE") # Remove excluded journals

@@

# PPC policy by COPE membership status (prominent sample)
```{r}

table_PPCbyCOPEprom <- dj_prominent %>%
  filter(ppc_type == "A" & is_empirical == TRUE) %>%
  count(has_ppc, cope)

print(table_PPCbyCOPEprom)

@@

# PPC policy by COPE membership status (random sample)
```{r}

table_PPCbyCOPErand <- dj_random %>%
  filter(ppc_type == "A" & is_empirical == TRUE) %>%
  count(has_ppc, cope)

print(table_PPCbyCOPErand)

@@

# Descriptives for each journal sample [**EDIT so these tables show ppc_type == "A" only**]
```{r}
table(dj_prominent$field, dj_prominent$has_ppc)
table(dj_random$field, dj_random$has_ppc)

table(dj_prominent$field, dj_prominent$cope)
table(dj_random$field, dj_random$cope)
```

# ANALYSIS

# Calculate CIs for YES [**EDIT TO DERIVE NUMBERS FROM DATA**]
Not sure if this makes sense to do for Prominent and Total, as these are not random samples
```{r}
library(binom)

@@

# Calculate CIs for NO [**EDIT TO DERIVE NUMBERS FROM DATA**]
```{r}
library(binom)

@@

table(d_journals$ppc_name)  #PPC names from all entries
table(d_journals$sample_id, d_journals$ppc_name) #PPC names from each sample

@@

# PPC length limitations (Prominent)
```{r}

table(dj_prominent$ppc_length, dj_prominent$ppc_name)

```
# PPC length limitations (Random)
```{r}

table(dj_random$ppc_length, dj_random$ppc_name)

```
# PPC time limitations (Prominent)
``` {r}

table(dj_prominent$ppc_time, dj_prominent$ppc_name)

@@

# PPC time limitations (Random)
```{r}

table(dj_random$ppc_time, dj_random$ppc_name)

@@

# Create and combine restiction statement graphs with ppc acceptance (prominent sample)
```{r}

# Filter and transform restrictions for ppc_length
ppc_length_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>% # removes Archive Only PPC types
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>% 
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and transform restrictions for ppc_time
ppc_time_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data <- bind_rows(
  ppc_length_data %>% mutate(Code = "Length"),
  ppc_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

# Create the first graph
graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")

# Create the second graph
graph2 <- dj_prominent %>%
  filter(ppc_type == "A") %>% # Keeps only first PPC row for each journal
  filter(!is.na(has_ppc)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Archive',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes',
    TRUE ~ has_ppc
  )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

# Arrange both graphs in the same figure
combined_plots <- graph2 + graph1
combined_plots

ggsave(filename = "Prominent_statements.png", plot = last_plot(), device = "png")
```
# Create and combine restiction statement graphs with ppc acceptance (random sample)
```{r}

# Filter and process data for ppc_length
ppc_length_random <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and process data for ppc_time
ppc_time_random<- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data_random <- bind_rows(
  ppc_length_random %>% mutate(Code = "Length"),
  ppc_time_random %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

# Create the first graph
graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")

# Create the second graph
graph3 <- d_journals %>%
  filter(sample_id == "random" | sample_id == "both") %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(has_ppc)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Archive',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes',
    TRUE ~ has_ppc
  )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

# Arrange both graphs in the same figure
combined_plots <- graph3 + graph4
combined_plots

ggsave(filename = "Random_statements.png", plot = last_plot(), device = "png")

@@

# Restriction Statements Graph
```{r}

@@

```{r}
count_non_missing <- sum(!is.na(dj_prominent$ppc_length))
cat("Count of non-missing values in ppc_length:", count_non_missing, "\n")
```

@@

#Coder Disagreements
```{r}

d_journals %>%
  filter(coder_id != "FINAL (TEH)") %>%

@@

# PREVALENCE ESTIMATES

# Calculate CIs for preavalence [**EDIT TO IMPORT VALUES FROM DATA**]
```{r}
library(binom)

# Prominent Sample data for linked
plPPCsuccess <- 1 #PPC events in prominent sample
rlPPCsuccess <- 0 #PPC events in random sample
linkedSample <- 101 #total sample size

# GRAPH FOR PRESENTATION
# PPC Policy by Sample
